%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD in Computer Vision} % Degree
    {Autonomous University of Barcelona} % Institution
    {Barcelona, Spain} % Location
    {2011--(2016)} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Supervised by: \href{http://vi.cvc.uab.es/fernando-vilarino}{Dr. Fernando Vilari\~no}.}
        \item {Working on \textbf{natural light (webcam-based) eye tracking algorithms}.}
        \item {Making the tracker more accurate, robust and easier to use.}
        \item {Collaborating with \href{http://ablab.org}{Dan Norton} for \textbf{interdisciplinary projects}.}
        \item {Using computer vision and eye tracking to create artistic user interactions.}
        \item {Presented joint project Memory Fields in \textbf{\href{http://sonarplusd.com/}{Sonar +D 2015}} and \href{http://l3.cvc.uab.es/}{The Volpelleres Living Lab}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {MSc in Computer Vision and Artificial Intelligence} % Degree
    {Autonomous University of Barcelona} % Institution
    {Barcelona, Spain} % Location
    {2011--2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Courses on many areas of computer vision.}
        \item {Hands-on experience in fields including \textbf{image processing}, \textbf{machine learning} and \textbf{artificial intelligence}.}
        \item {Final project on natural light eye trackers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {BSc in Computer Engineering} % Degree
    {Bogazici University} % Institution
    {Istanbul, Turkey} % Location
    {2004--2009} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {One of the top computer engineering degrees (top \textbf{0.03 percentile} in university entrance exams).}
        \item {Courses on \textbf{robotics}, \textbf{artificial intelligence} (MSc level), \textbf{pattern recognition} (MSc level) in the senior year.}
        \item {Final project on \textbf{reinforcement learning} for Aibo robots (simulation environment).}
        \item {Also studied: biomedical engineering, Spanish (3 years), linguistics, advanced English, environmental science.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
