%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Banksoft - Payment Systems Solutions} % Organization
    {Istanbul, Turkey} % Location
    {2009--2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on personalization (preparation for customers) of \textbf{EMV-compliant chip cards} for major Turkish and international banks.}
        \item {Completed training on programming \textbf{embedded applications} for EMV chip cards.}
        \item {Actively participated in the project revolutionizing the company's legacy systems.}
        \item {\textit{Defined tasks:}}
        \begin{itemize}
            \item Managing customer data and \textbf{security data}.
            \item Preparing TLV-format (tag-length-value) file outputs for \textbf{mass-embossing of cards}.
            \item Reflecting the required changes for new card products (changed chips, new campaigns, etc.) to the code.
            \item Installing updated components on production servers of banks.
        \end{itemize}
        \item {\textit{Additional accomplishments:}}
        \begin{itemize}
            \item Developed a program for internal use of colleagues while development.
            \item Developed an editor for parsing TLV format personalization files. Implemented functionalities for \textbf{editing}, \textbf{automated verification} of security data, parsing of special tag values, robust error detection, etc.
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack Developer} % Job title
    {Imovasyon} % Organization
    {Istanbul, Turkey} % Location
    {2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in the development of startup's \textbf{QR code} management system (cepkod.com).}
        \item {Connected the system with Microsoft Tag, Facebook, SMS sending APIs.}
        \item {Developed an \textbf{API} to allow simultaneous creation and management of QR codes and Microsoft Tags.}
        \item {Developed a \textbf{URL shortener} system to compress data encoded in the QR codes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack Developer} % Job title
    {Inveon} % Organization
    {Istanbul, Turkey} % Location
    {2008--2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on \textbf{C\#} web projects for internal use of many large Turkish companies.}
        \item {Projects for a \textbf{variety of sectors} (pharmaceutics, insurance, security, etc.).}
        \item {Learned latest web technologies (jQuery, AJAX, etc.) and practiced \textbf{agile development} methodology.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
