%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\cvsubsection{Journal Articles}

\paragraphstyle{
\textbf{Onur Ferhat}, Fernando Vilariño (2016). \textbf{Low Cost Eye Tracking: Methods and General Applications}. Journal of Computational Intelligence and Neuroscience. (under review)

\textbf{Onur Ferhat}, Fernando Vilariño, F. Javier Sanchez. (2014). \textbf{A Cheap Portable Eye-Tracker Solution for Common Setups}. Journal of Eye Movement Research, 7(3), 1–10.
}
\\

\cvsubsection{Conference Proceedings}

\paragraphstyle{
\textbf{Onur Ferhat}, Arcadi Llanza, Fernando Vilari\~no. (2015). \textbf{Gaze Interaction for Multi-Display Systems using Natural Light Eye-Tracker}. In 2nd International Workshop on Solutions for Automatic Gaze Data Analysis.

Dan Norton, Fernando Vilari{\~n}o, \textbf{Onur Ferhat}. (2015). \textbf{Creative Engagement in Digital Collections}. In Internet Librarian International.

Dan Norton, Fernando Vilari{\~n}o, \textbf{Onur Ferhat}. (2015). \textbf{Memory Fields: DJs in the Library}. In 21st International Symposium on Electronic Art (accepted).

\textbf{Onur Ferhat}, Arcadi Llanza, Fernando Vilari\~no. (2015). \textbf{A Feature-Based Gaze Estimation Algorithm for Natural Light Scenarios}. In 7th Iberian Conference on Pattern Recognition and Image Analysis (Vol. 9117, pp. 569–576). Springer International Publishing.

\textbf{Onur Ferhat}, Fernando Vilariño. (2013). \textbf{A Cheap Portable Eye-Tracker Solution for Common Setups}. In 17th European Conference on Eye Movements.}
\\

\cvsubsection{Master's Thesis}

\paragraphstyle{
\textbf{Onur Ferhat}. (2012). \textbf{Eye-Tracking with Webcam-Based Setups: Implementation of a Real-Time System and an Analysis of Factors Affecting Performance}. (Fernando Vilari\~no, Ed.) (Vol. 172).
}